Pandemic Pass? Treaty Derogations and Human Rights Practices During COVID-19

### 2024-09-22 README.qmd
Add instructions for XQuartz

2. [Install R](https://cloud.r-project.org/) (and preferably [RStudio](https://www.rstudio.com/products/rstudio/download/#download)).
    - If you're using macOS, [install XQuartz too](https://www.xquartz.org/), so that you have access to the Cairo graphics library
    - If you’re using Windows, [install RTools too](https://cran.r-project.org/bin/windows/Rtools/) and add it to your PATH so that you can install packages from source if needed

>>>>

2. [Install R](https://cloud.r-project.org/) (and preferably [RStudio](https://www.rstudio.com/products/rstudio/download/#download)).
    - If you're using macOS, [install XQuartz too](https://www.xquartz.org/), so that you have access to the Cairo graphics library. Also [install Homebrew](https://brew.sh/) and run `brew install ghostscript`.
    - If you’re using Windows, [install RTools too](https://cran.r-project.org/bin/windows/Rtools/) and add it to your PATH so that you can install packages from source if needed
